A Constraint Solving Approach to Parikh Images of Regular Languages

### 2024-02-21 calculus.tex
Clarify backward propagation, dom()
Closes: #81

>>>>

The $\Dominates$~relation can be efficiently implemented in a solver
by using standard Ford-Fulkerson\slash{}Edmonds-Karp min-cut between a state
and the initial state after removing transitions where $\Filter(\Transition) = 0$.
By only performing this computation after such filtering, a solver additionally avoids
breaking the rule of adding clauses that already appear in the formula.

We here only define forward propagation. Backward propagation 
can be straightforwardly obtained by computing reachability from
an accepting state on the same principle as above, and indeed our
implementation of \Calculus{} does this.
